Modeling a declining count variable

### 2024-06-22 src/count_completed.Rmd
Update 2008, part 2
Update 2008 files, part 3

```{r md_links}
c_text <- "page_update: "
md_files$page_update_line <- "999"
for (i_row in 1:nrow(md_files)) {
  full_file_name <- glue("{md_path}/{md_files$yr[i_row]}/{md_files$fn[i_row]}")
  read_lines(full_file_name) %>%
    str_subset(fixed(c_text)) %>%
    paste0("", collapse=", ") -> md_files$page_update_line[i_row]
}
count(md_files, page_update_line)
count(md_files, yr, page_update_line)
```

>>>>

```{r md_links}
c_text <- "page_update: "
f_text <- "[sim1]: "
md_files$page_update_line <- "999"
md_files$old_link <- "999"
for (i_row in 1:nrow(md_files)) {
  full_file_name <- glue("{md_path}/{md_files$yr[i_row]}/{md_files$fn[i_row]}")
  read_lines(full_file_name) -> file_text
  file_text %>%
    str_subset(fixed(c_text)) %>%
    str_replace(fixed(c_text), "") -> page_update
  file_text %>%
    str_subset(fixed(f_text)) %>%
    str_replace(f_text, "") %>%
    paste0("") %>%
    paste0(collapse=", ") -> old_link
  n <- length(page_update)
  if (n > 1) {
    cat(
      glue(
        "\n\n{n} duplicates found in {full_file_name}.\n\n"))}
  page_update %>%
    paste0("", collapse=", ") -> md_files$page_update_line[i_row]
  md_files$old_link[i_row] <- old_link
}
count(md_files, page_update_line)
# count(md_files, yr, page_update_line)
```

```{r}
for (y in subdir_list) {
  md_files %>%
    filter(yr==y) %>%
    count(yr, page_update_line) %>%
    print
  cat("\n\n")
}
```

### Pages with page_update = `r (update_text="n")`

```{r}
for (y in subdir_list) {
  md_files %>%
    filter(yr==y) %>%
    filter(page_update_line==update_text) %>%
    select(-old_link) %>%
    print
  cat("\n\n")
}
```

### Pages with page_update = `r (update_text="partial")`

```{r}
for (y in subdir_list) {
  md_files %>%
    filter(yr==y) %>%
    filter(page_update_line==update_text) %>%
    select(-old_link) %>%
    print
  cat("\n\n")
}
```

### Pages with page_update = `r (update_text="complete")`

```{r}
for (y in subdir_list) {
  md_files %>%
    filter(yr==y) %>%
    filter(page_update_line==update_text) %>%
    select(-old_link) %>%
    print
  cat("\n\n")
}
```

### Pages with page_update = `r (update_text="")`

```{r}
for (y in subdir_list) {
  md_files %>%
    filter(yr==y) %>%
    filter(page_update_line==update_text) %>%
    select(-old_link) %>%
    print
  cat("\n\n")
}
```

### Pages with links to previous site

```{r}
for (y in subdir_list) {
  md_files %>%
    filter(yr==y) %>%
    filter(length(old_link) > 0) %>%
    select(yr, old_link) %>%
    print
  cat("\n\n")
}
```

### Pages without links to previous site

```{r}
for (y in subdir_list) {
  md_files %>%
    filter(yr==y) %>%
    filter(length(old_link) == 0) %>%
    select(yr, old_link) %>%
    print
  cat("\n\n")
}
```

```{r}
test1 <- paste0("## ", 1:5, collapse="\n\n")
```

`r test1`

```{r}
#| results: asis
cat(r'(
# Header

Text
)')
```

```{r}
#| results: asis
cat(r'(\n# Header\n\nText]\n)')
```

### 2024-06-22 text/08/declining-count-model.Rmd
Update 2008 files, part 3

---
title: Modeling a declining count variable
author: Steve Simon
date: 2008-06-14
categories:
- Blog post
tags:
- Poisson regression
output: html_document
---
I've been working on an interesting project that requires Poisson
regression. A company sends out a mailing and gets a certain number of
telephone calls back on each of the days following. The number of phone
calls is typically (but not always) highest on the first day afterwards
and declines rapidly on successive days. I wanted to develop a simple
Poisson regression model for this data.

>>>>

---
title: Modeling a declining count variable
author: Steve Simon
date: 2008-06-14
categories:
- Blog post
tags:
- Being updated
- Poisson regression
output: html_document
page_update: partial
---
I've been working on an interesting project that requires Poisson
regression. A company sends out a mailing and gets a certain number of
telephone calls back on each of the days following. The number of phone
calls is typically (but not always) highest on the first day afterwards
and declines rapidly on successive days. I wanted to develop a simple
Poisson regression model for this data.
